Live Functional Programming with Typed Holes

### 2018-02-26 calculus.tex
fig-complete

\autoref{fig:complete} defines complete types and expressions...

\begin{theorem}[Complete Progress \cy{??}]
If $\hcomplete{\hexp}$ and
$\expandSyn{\emptyset}{\hexp}{\htau}{\dexp}{\Delta}$ then either
$\isValue{\dexp}$ or $\stepsToD{\Delta}{\dexp}{\dexp'}$ for some $\dexp'$.

\end{theorem}

\begin{theorem}[Complete Preservation \cy{??}]
If $\hcomplete{\hexp}$ and
$\expandSyn{\emptyset}{\hexp}{\htau}{\dexp}{\Delta}$ and
$\stepsToD{\Delta}{\dexp}{\dexp'}$ then
$\hasType{\Delta}{\emptyset}{\dexp'}{\htau}$
\end{theorem}

>>>>

\autoref{fig:complete} defines \emph{complete} H-types, H-expressions, and
dynamic H-expressions to be those terms without type or expression holes.

\begin{theorem}[Complete Progress]
  If $\hasType{\hDelta}{\emptyset}{\dexp}{\htau}$
  and $\isComplete{\dexp}$
  then either $\stepsToD{}{\dexp}{\dexp'}$
  or $\isValue{\dexp}$.
\end{theorem}

\begin{theorem}[Complete Preservation]
  If $\hasType{\hDelta}{\emptyset}{\dexp}{\htau}$
  and $\isComplete{\dexp}$
  and $\stepsToD{}{\dexp}{\dexp'}$
  then $\hasType{\hDelta}{\emptyset}{\dexp'}{\htau}$.
\end{theorem}

\begin{theorem}[Complete Expansion] ~
  \begin{enumerate}
    \item
      If $\isComplete{\hexp}$
      and $\expandSyn{\hGamma}{\hexp}{\htau}{\dexp}{\Delta}$
      then $\isComplete{\dexp}$.
    \item
      If $\isComplete{\hexp}$
      and $\expandAna{\hGamma}{\hexp}{\htau}{\dexp}{\htau'}{\Delta}$
      then $\isComplete{\dexp}$.
  \end{enumerate}
\end{theorem}
